\section{Operational Reality: The Hybrid Deployer}

\subsection{The Mixture-of-Experts (MoE) Architecture}
Transitioning this model from a theoretical notebook to an operational Space Operations Center (SpOC) requires strict fail-safes. The neural network must never degrade baseline predictions during nominal space weather conditions. To achieve this, we developed a rule-based Hybrid Mixture-of-Experts (\texttt{HybridDeployer}).

The Deployer loads two distinct G-PINN models:
\begin{enumerate}
    \item \textbf{Quiet Expert:} Trained exclusively on non-storm data (9 input features, excluding F10.7 to prevent overfitting to noisy minor solar variations).
    \item \textbf{Storm Expert:} Trained to handle massive drag variations (10 input features, including F10.7 and high $K_p$ data vectors).
\end{enumerate}

\subsection{Algorithmic Routing}
The system constantly polls live space weather APIs. Let the live observed solar flux be $F_{\text{live}}$. The SpOC defines a critical threshold, $F_{\text{thresh}} = 120.0$.
\begin{algorithm}[H]
\caption{Hybrid SpOC Routing}
\begin{algorithmic}[1]
\REQUIRE $TLE_1$, $TLE_2$, $t_{target}$
\STATE $F_{live} \leftarrow \text{Fetch Celestrak API}$
\STATE $[\mathbf{r}, \mathbf{v}] \leftarrow \text{SGP4}(TLE, t_{target})$
\IF{$F_{live} < F_{\text{thresh}}$}
    \STATE $\mathcal{M} \leftarrow \text{Quiet Expert G-PINN}$
    \STATE $\mathbf{x}_{feat} \leftarrow [\mathbf{r}, \mathbf{v}, B^*, \dot{n}, \Delta t]$
\ELSE
    \STATE $\mathcal{M} \leftarrow \text{Storm Expert G-PINN}$
    \STATE $\mathbf{x}_{feat} \leftarrow[\mathbf{r}, \mathbf{v}, B^*, \dot{n}, \Delta t, F_{live}]$
    \STATE $\text{ALERT:} \text{ Storm protocol activated}$
\ENDIF
\STATE $\hat{\mathbf{y}}_{corr} \leftarrow \mathcal{M}(\mathbf{x}_{feat}) \cdot \tanh(5 \cdot \Delta t_{norm})$
\STATE $\mathbf{r}_{final} \leftarrow \mathbf{r} + \hat{\mathbf{y}}_{corr}$
\RETURN $\mathbf{r}_{final}$
\end{algorithmic}
\end{algorithm}

This hard-coded bifurcation guarantees mathematical safety. The Quiet Expert relies purely on local state-vector kinematics, respecting the SGP4 baseline. When extreme weather hits, the Storm Expert is triggered, aggressively pulling the satellite back along-track to compensate for unmodeled thermospheric drag.
